final_project_draft

### 2022-04-06 draft.Rmd
April 6th graded after class commit. Made a few improvements.

library(plotly)
```

@@

plot1 <- ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point() +
  labs(x = " ", 
       y = " ",
       title = "What Influence Could NFL Team Owners Have on Elections?",
       colour = "Political Party") +
  scale_colour_viridis_d() +
  theme_bw()

ggplotly(plot1, tooltip = "label")

ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point(size = 3) +
  labs(x = " ", 
       y = " ",
       title = "How Much Did NFL Owners Donate in 2016?",
       colour = "Political Party",
       subtitle = "What Influence Could NFL Team Owners Have on Elections?") +
  scale_colour_viridis_d() +
  theme_bw() +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 15,
                                  margin = margin(c(t = 20,
                                                    b = 50,
                                                    vjust = 10))),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 10),
        legend.title = element_text(family = "mono",
                                    face = "bold",
                                    size = 8),
        legend.text = element_text(family = "mono",
                                   size = 8),
        axis.text = element_text(family = "mono",
                                 size = 8),
        legend.box.background = element_rect(),
        legend.position = "bottom")
```

@@

ggplot(data = frequent, aes(x = amount, y = Owner, label = Amount, colour = Party)) +
  geom_point() +
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_brewer(palette = "Dark2") +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 12,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text.x = element_text(family = "mono"),
        axis.text.y = element_text(family = "mono"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 7),
        legend.text = element_text(family = "mono",
                                   size = 6),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 9,
                                     vjust = 5),
        legend.box.just = "left",
        legend.box.background = element_rect())

plot2 <- ggplot(data = frequent, aes(x = amount, y = Owner, label = Recipient, colour = Party)) +
  geom_point() +
  labs(title = "How Much Do They Donate & To Who?",
       y = "Owners",
       x = "Amount Donated",
       colour = "Party") +
  theme_grey() +
  scale_colour_brewer(palette = "Dark2") +
  theme(legend.position = "bottom")

ggplotly(plot2, tooltip = "label")

test <- frequent %>% mutate(owner = fct_reorder(.f = Owner, .x = n))
test2 <- frequent %>% mutate(owner = fct_inorder(Owner))
```

@@

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  scale_fill_viridis_d() +
  labs(title = "Is There Any Political Party Receiving More Support From Charles Johnson?",
       x = " ",
       y = "Count of Donations") +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  hjust = 0.5,
                                  size = 13,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_text(family = "mono",
                                    size = 9,
                                    face = "italic",
                                    margin = margin(t = 20))) +
  geom_label(data = cj_party, aes(label = n), show.legend = FALSE,
             label.size = 1)
```

@@

ggplot(data = recipients, aes(x = recipient, y = n, colour = Party)) +
  geom_point() +
  geom_segment(aes(x = recipient, xend = recipient, y = 0, yend = n)) +
  coord_flip() +
  labs(x = " ",
       y = "Count of Donations") +
  labs(title = "Organizations Receiving Most Donations Across All Leagues") +
  scale_colour_brewer(palette = "Dark2") +
  theme(legend.position = "bottom") +
  scale_x_discrete(labels = new_names) +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono",
                                  size = 8),
        axis.title.x = element_text(size = 10,
                                    margin = margin(t = 20,
                                                    b = 10)),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
         legend.box.background = element_rect())
```

@@

plot6

ggplot(data = blockbusters1, aes(x = release_year, y = imdb_rating, colour = mpaa_rating,
                                          label = Film)) +
  geom_point() +
  facet_wrap(~mpaa_rating) +
  geom_smooth(se = FALSE, method = 'lm') +
  labs(y = "IMDB Rating",
       x = "Release Year",
       colour = "MPAA Rating",
       title = "Blockbuster Ratings: 1977 to 2019") +
  theme_hc() +
  scale_colour_brewer(palette = "Dark2") +
  theme(plot.title = element_text(family = "mono",
                                  face = "italic",
                                  margin = margin(t = 20, b = 20)),
        axis.ticks = element_blank(),
        axis.title = element_text(family = "mono",
                                  face = "italic"),
        axis.text = element_text(family = "mono"),
        legend.box.background = element_rect(),
        legend.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "italic"),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.title.x = element_text(margin = margin(t = 20, b = 10)),
        strip.text = element_text(family = "mono",
                                  face = "bold"))
```

>>>>

library(plotly)
options(scipen = 10)
## install.packages("ggpmisc")
library(ggpmisc)
```

@@

ggplot(data = high_donations, aes(x = amount, y = owner_ordered, label = Recipient, colour = party)) +
  geom_point(size = 2) +
  labs(x = " ", 
       y = " ",
       title = "How Much Did NFL Owners Donate in 2016?",
       colour = "Political Party",
       subtitle = "What Influence Could NFL Team Owners Have on Elections?") +
  scale_colour_viridis_d() +
  theme_bw() +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 15,
                                  margin = margin(c(t = 20,
                                                    b = 50,
                                                    vjust = 10))),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 10),
        legend.title = element_text(family = "mono",
                                    face = "bold",
                                    size = 8),
        legend.text = element_text(family = "mono",
                                   size = 8),
        axis.text = element_text(family = "mono",
                                 size = 8),
        legend.box.background = element_rect(),
        legend.position = "bottom") 
```

@@

level_order <- factor(frequent$Owner, level = c('Stephen M. Ross', 'Herbert Simon',
                                                'Jerry Reinsdorf', 'Ken Kendrick',
                                                'Jimmy and Susan Haslam',
                                                'Jody Allen (Paul G. Allen Trust)',
                                                'Dan DeVos', 'John Rogers',
                                                'Micky Arison', 'Charles Johnson'))

ggplot(data = frequent, aes(x = amount, y = level_order, label = Amount, colour = Party)) +
  geom_point() +
  labs(title = "How Many Donations Have They Made?",
       subtitle = "Examining The Monetary Amount of Observed Political Donations",
       y = " ",
       x = " ",
       colour = "Party") +
  scale_colour_brewer(palette = "Dark2") +
    theme_bw() +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  size = 12,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text.x = element_text(family = "mono"),
        axis.text.y = element_text(family = "mono"),
        legend.title = element_text(family = "mono", 
                                    face = "bold",
                                    size = 7),
        legend.text = element_text(family = "mono",
                                   size = 6),
        plot.subtitle = element_text(family = "mono",
                                     face = "italic",
                                     size = 9,
                                     vjust = 5),
        legend.box.just = "left",
        legend.box.background = element_rect())
```

@@

level_order2 <- factor(charles_johnson$Party, level = c('Republican', 'Democrat', 'Bipartisan, but mostly Republican'))

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  scale_fill_viridis_d(option = "plasma") +
  labs(title = "Is There Any Political Party Receiving More Support From Charles Johnson?",
       x = " ",
       y = "Count of Donations") +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  hjust = 0.5,
                                  size = 13,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_text(family = "mono",
                                    size = 9,
                                    face = "italic",
                                    margin = margin(t = 20)))

table <- data.frame(Party = rep(c("Republican", "Bipartisan, but mostly Republican",
                                "Democrat", each = 1),
                              Count = rep(c("207", "4", "2"), 1)))
table

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col() + 
  annotate(geom = "table") +
  coord_flip()
```

@@

ggplot(data = recipients, aes(x = recipient, y = n, colour = Party)) +
  geom_point() +
  geom_segment(aes(x = recipient, xend = recipient, y = 0, yend = n)) +
  coord_flip() +
  labs(x = " ",
       y = "Count of Donations") +
  labs(title = "Organizations Receiving Most Donations Among All Owners") +
  scale_colour_brewer(palette = "Dark2") +
  theme(legend.position = "bottom") +
  scale_x_discrete(labels = new_names) +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono",
                                  size = 8),
        axis.title.x = element_text(size = 10,
                                    margin = margin(t = 20,
                                                    b = 10)),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
         legend.box.background = element_rect())

pol_donations %>% group_by(League) %>%
  summarise(n = n()) %>%
  arrange(desc(n))
```

@@

ggplot(data = blockbusters1, aes(x = release_year, y = imdb_rating, colour = mpaa_rating,
                                          label = Film)) +
  geom_point() +
  facet_wrap(~mpaa_rating) +
  geom_smooth(se = FALSE, method = 'lm') +
  labs(y = "IMDB Rating",
       x = "Release Year",
       colour = "MPAA Rating",
       title = "Blockbuster Ratings: 1977 to 2019") +
  theme_hc() +
  scale_colour_brewer(palette = "Dark2") +
  theme(plot.title = element_text(family = "mono",
                                  face = "italic",
                                  margin = margin(t = 20, b = 20)),
        axis.ticks = element_blank(),
        axis.title = element_text(family = "mono",
                                  face = "italic"),
        axis.text = element_text(family = "mono"),
        legend.box.background = element_rect(),
        legend.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "italic"),
        axis.title.y = element_text(margin = margin(r = 20)),
        axis.title.x = element_text(margin = margin(t = 20, b = 10)),
        strip.text = element_text(family = "mono",
                                  face = "bold"))

blockbusters %>% group_by(mpaa_rating) %>%
  summarise(n = n()) %>%
  filter(!is.na(mpaa_rating))
```
